---
title: "Midterm"
author: "Cameron Snyder"
date: "March 3, 2019"
output: html_document
---

```{r}
library(tidyverse)
```

# The tidyverse packages
1. Can you name which package is associated with each task below?
Plotting -  ggplot2
Data munging/wrangling - dplyr
Reshaping (speading and gathering) data - dplyr
Importing/exporting data -  ??

2 Now can you name two functions that you've used from each package that you listed above for these
tasks?
Plotting - ggplot()
Data munging/wrangling -select()
Reshaping data - cast()
Importing/exporting data - read.csv()

# R Basics
1. 
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2 , 3 )
```
2
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
```
3. The values inthe vector are a mix of integers and characters but display as string

# Data import/export
1.
```{r}
data_import_txt <- read.delim("C:/Users/cameron.snyder/Documents/Metrics/Reports/rail_trail.txt")
```

```{r}
glimpse(data_import_txt)
```


2.
```{r}
data_import <- read.csv("C:/Users/cameron.snyder/Documents/Metrics/Reports/rail_trail.csv")
```
```{r}
glimpse(data_import)
```


# Visualization
1. There are no labels on what would be the y axis of age and gender. The sizes aren't clear if their reporesentative of the whole population or along the y axis
2

```{r}
ggplot(diamonds, aes(cut, carat)) +
  geom_boxplot(aes(fill = color)) +
  coord_flip()
```
3?

# Data munging and wrangling
1. To be tidy, each variable must have its own column, each observation have its own row, and each value have its own cell. It is not tidy because count is not its own variable in a column - see multiple types per count. We can fix this by spreading
```{r}
table2 %>%
    spread(key = type, value = count)
```


2. 
```{r}

price_per_carat <- mutate(diamonds, price_per_carat = diamonds$price/diamonds$carat)

glimpse(price_per_carat)

```

3.  How Many diamonds apply to filter:
```{r}
question_3 <- filter(diamonds, price > 10000 & carat < 1.5)
count(question_3)
```
What proportion?
```{r}
834/ count(diamonds)
```
Do the results make sense? the proportion of 1.5% of diamonds are more than $10,000 and with a carat lower than 1.5 make sense. The lower the carat the higher the value, these would be rare and valuable

We need to be wary of these numbers because the correlation isn't explained with a proportion of # of filter / # of total

# EDA

```{r}
glimpse(txhousing)
```
1. the date range is between 2000-2015
```{r}
max(txhousing$year)
```
2. 90 unique cities
```{r}
unique(txhousing$city)
```
3. Houston, Texas in July 2015 had the highest number of sales
```{r}
filter(txhousing, sales >= 8945)
```
4. I predict it's a positive correlation between the number of listings and the number of sales
```{r}
ggplot(data = txhousing, aes(y = sales, x = listings)) + geom_point() + geom_smooth()
```
5 ?

6. 
```{r}
xx <- filter(txhousing, sales >= 500)
ggplot(data = xx, aes(x = median, y = city)) + geom_point()
```
- The distributions of median sales by city are different
- Corpus Christi likely needs more data
- The distribution of median sales over 500 will have a big spread and lots of data points

# Git and Git Hub
1. https://github.com/Cameronlane11/compscix-415-2-assignments


